Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-12-26 manuscript.Rmd
Address reviewer comments pt. 2

## Data Preparation
### Social Cohesion Metric
The social cohesion or linguistic similarity of daily tweets was calculated by quantifying the frequency of shared content words with respect to those words’ frequencies in the entire tweet corpus. Retweets were included in the corpus and used in the social cohesion calculation, as they indicate strong support for an individual’s message. Stop words, punctuations, and duplicate words were not removed from the tweets. The lengths of tweets were disregarded, as the aspect of interest is in shared linguistic content and not breadth of description.

>>>>

## Data Preparation
### Social Cohesion Metric
The social cohesion or linguistic similarity of daily tweets was calculated by quantifying the frequency of shared content words with respect to those words’ frequencies in the entire tweet corpus. Retweets were included in the corpus and used in the social cohesion calculation, as they indicate strong support for an individual’s message. Stop words, punctuations, and duplicate words were not removed from the tweets. The lengths of tweets were disregarded, as the aspect of interest is in shared linguistic content and not breadth of description. The presence of bots was not investigated. According to a 10-Q report for Twitter, Inc., for a quarterly period in 2014, the estimated number of third party applications automatically contacting the servers (i.e., bots), was less than 8.5% [@twitter2014]. As the data in this study were collected two years prior, this number was likely even less. Thus we consider the number of bots negligible for the present investigation.
